Using traffic analysis to identify The Second Generation Onion Router

### 2010-12-31 thesis/experiment.tex
Some more software summaries

\section{Personal Computer}

\section{Hub/Unmanaged Router}
\section{Tor Software}
\section{'tcpdump' Software}
\section{Weka Software}
\section{VirtualBox Software}
\section{Ruby Software}

\section{Ubuntu Linux Software}

@@

\section{Selenium Software}

@@

\section{Firefox Software}

Firefox is a web browser developed by the Mozilla organization and freely
available for most desktop personal computers \parencite{mozilla}. It's strong
standards compliance \parencite{Hammond:2010fk} and popularity
\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal candidate for
this experiment .

\section{OpenSSH Software}

\cite{Tucker:2010ly}
\cite{:2010zr}
\cite{:ve}

\section{Apache Software}

@@

\section{Sinatra Software}

\section{Hardware Configuration}

@@

\section{Software Configuration}

>>>>

\subsection{Personal Computer}

Four computer systems were employed each with the same specifications.

\subsection{Hub/Managed Router}

The network equipment chosen to run the experiment is a simple hub or
'repeater' which duplicates all packets transmitted on all ports. This makes it
easy to monitor all communications across the network for analysis purposes
\parencite{website:hub-reference}.

\subsection{Tor Software}

\subsection{'tcpdump' Software}

The tcpdump software captures network packets that are transferred using
network interfaces attached to the current hardware \parencite{:2009cr}.  It is
available on most operating systems and supports a flexible filtering language
for capturing only the specific packets desired. The format of output produced
by tcpdump is well documented \parencite{:nx} which makes it ideal for
transformation and processing by third party tools.

\subsection{Weka Software}

Weka is data mining software which includes tools for classification of data
sources using a wide variety of machine learning algorithms
\parencite{Hall:2009p7662}.

\subsection{VirtualBox Software}

VirtualBox is virtualization software that allows the running of a guest
operating system in its own environment on another host operating system
\parencite{:fk}.  It supports snapshots and a remote control facility which
make it useful for running repetitions in an experimental environment
\parencite{:uq}.

\subsection{Ruby Software}

Ruby is an object orientated, dynamic programming language which is useful for
quick prototyping and as such has been used to automate the simulation
described in this experiment \parencite{:2010uq}.

(I used it because it is a language that is fast to develop in and I am
familiar with it)

\subsection{Ubuntu Linux Software}

@@

\cite{:2010ly}

\subsection{Selenium Software}

@@

\subsection{Firefox Software}

Firefox is a web browser developed by the Mozilla organization and freely
available for most desktop personal computers \parencite{mozilla}. It's strong
standards compliance \parencite{Hammond:2010fk} and popularity
\parencite{:2010kx,:2010vn} on the simulation platform make it an ideal
candidate for this experiment.

\subsection{OpenSSH Software}

OpenSSH is a freely available suite of connectivity tools
\parencite{:2010zr,:ve} that supports remote command execution
\parencite{Tucker:2010ly}.

\cite{:2010zr}

\subsection{Apache Software}

@@

\subsection{Sinatra Software}

Sinatra is a simple framework for creating dynamic web applications using the
Ruby programming language \parencite{:2010bh}.

\subsection{Hardware Configuration}

@@

\subsection{Software Configuration}
